---
title             : "The Sound of Intellect: Speech Reveals a Thoughtful Mind, Increasing a Job Candidate’s Appeal"
shorttitle        : "Speech Increases a Job Candidate’s Appeal"

author: 
  - name          : "Kamal Abdelrahman"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "kamalabdel97@gmail.com"

affiliation:
  - id            : "1"
    institution   : "City University of New York - Brooklyn College"

authornote: |
  Kamal Abdelrahman is an undergraduate at the City University of New York - Brooklyn College in Brooklyn, NY majoring in psychology with a focus in statistical programming


abstract: |
 This study is an exact replication of Juliana Schroeder & Nicholas Epley's (2015) experiment of whether a potential job candidate is percieved more intelligent through text or audio. 39 Forturne 500 company recruiters rated job candidates on their intellect, a composite score of the candidate's intelligence, competence, and thoughtfulness. They hypothesized that speech communicates intelligence better than written words.  This study recreated the analysis of regarding presenation of pitches and their favorability. Analysis supported that hypothesis.


  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "replication, R, employment, communication"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library(papaja)
library(data.table)
library(MOTE)
library(scales)
library(ggplot2)
SmarterTalkerSpeaker<-fread("https://raw.githubusercontent.com/CrumpLab/statisticsLab/master/data/SchroederEpley2015data.csv")
SmarterTalkerSpeaker$gender <- as.factor(SmarterTalkerSpeaker$gender)
SmarterTalkerSpeaker$CONDITION <- as.factor(SmarterTalkerSpeaker$CONDITION)

```


```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



# Methods

*Participants*

In this study, there were `r (NROW(SmarterTalkerSpeaker))` participants, all professional Fortune 500 recruiters. The average of the recruiters was *M* = `r mean(SmarterTalkerSpeaker$age, na.rm = T)` (*SD* = -`r sd(SmarterTalkerSpeaker$age, na.rm = T)`). `r scales:: percent(length(which(SmarterTalkerSpeaker$gender == 1))/length(SmarterTalkerSpeaker$gender))` of the participants are male and `r scales:: percent(length(which(SmarterTalkerSpeaker$gender == 2))/length(SmarterTalkerSpeaker$gender))` are female. 

*Materials*

Two materials were used in this analysis. The first material was the dataset used in Schroeder & Epley's study from githhub. The data was analyzed so that the t-test could be reproduced. 

The second material was R Studio, the Integrated Development Environemnt (IDE) for R. The IDE was used as a platform to analyze the dataset in R. 


*Procedure*

To recreate this analysis of the t-test, the following steps were taken. First, the data was loaded into R from Github with the fread function from the data.table library. Then, a difference  
The data was retrieved from (website) and loaded into into a R via the fread function available under the data.table library (`r print(citation("data.table"))`) The data 

# Results
```{r, include = FALSE}
#T-Test
ConditionTTest <- t.test(SmarterTalkerSpeaker$like ~ SmarterTalkerSpeaker$CONDITION, var.eqqual = T)

M <- tapply(SmarterTalkerSpeaker$intell, SmarterTalkerSpeaker$CONDITION, mean)
stdev <- tapply(SmarterTalkerSpeaker$intell, SmarterTalkerSpeaker$CONDITION, sd)
N <- tapply(SmarterTalkerSpeaker$intell, SmarterTalkerSpeaker$CONDITION, length)
effectsize <- d.ind.t(M[1], M[2], stdev[1], stdev[2], N[1], N[2])
effectsize
```

An independent samples t-test was conducted to examine the manipulation effects of audio and written expressions of intelligence in potential employees. Interviewees who expressed their intelligence through spokem during their interviews were rated significantly better (*M* = `r mean(SmarterTalkerSpeaker$intell[SmarterTalkerSpeaker$CONDITION == 1])`, *SD* = `r sd(SmarterTalkerSpeaker$intell[SmarterTalkerSpeaker$CONDITION == 1])`) than interviewees who wrote out their responses (*M* = `r mean(SmarterTalkerSpeaker$intell[SmarterTalkerSpeaker$CONDITION == 0])`, *SD* = `r sd(SmarterTalkerSpeaker$intell[SmarterTalkerSpeaker$CONDITION == 0])`) `r apa_print(ConditionTTest)$statistic`, $d_{s}$ = `r apa(effectsize$d,2,T)`

# Discussion
Schroeder and Epley hypothesized that a person is a more appealing job candidate if they communicated with their voice as opposed to with text. Results supported this hypothesis, which stated that candidates who communicated through audio were rated significantly more desirable than canidates who did not. This analysis was consistent across all five experiments that were conducted. This is consistent with other literature that discusses  


\newpage

*Limitations*
The overall findings of the study indicated that candidates who communicated through audio as opposed to written text were rated significantly more intelligent. Though, after reexamining the 
 
*Implications*
The study explored the effects of various communication methods in regards to a person's desirability. This has potential for various avenues to be explored within the realm of communication. 

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
